PANCHANGE_analysis

### 2020-08-25 PANCHANGE_analysis.Rmd
added covid probable vs test cross table

## Cross table probable covid and covid test positive
```{r}
dat %>%
```

@@

dat <- dat %>%
  mutate(gad.change_binary =
           recode_factor(
             gad.change_binary_numeric,
             `1` = "Worsening",
             `2` = "No change",
             `3` = "Improvement"
           )
         )

@@

dat <- dat %>%
  mutate(phq.change_binary =
           recode_factor(
             phq.change_binary_numeric,
             `1` = "Worsening",
             `2` = "No change",
             `3` = "Improvement"
           )
  )

@@

dat <- dat %>%
  mutate(ocir.change_binary =
           recode_factor(
             ocir.change_binary_numeric,
             `1` = "Worsening",
             `2` = "No change",
             `3` = "Improvement"
           )
  )

>>>>

## Cross table probable covid and covid test positive
```{r Cross table probable covid and covid test positive}
dat %>%
  count(covid_test_positive, covid_probable_case_incl_screening) %>%
  spread(key = covid_test_positive, value = n)
```

@@

dat <- dat %>%
  mutate(gad.change_binary =
           recode_factor(
             gad.change_binary_numeric,
             `0` = "No change",
             `1` = "Worsening",
             `2` = "Improvement"
           )
         )

@@

dat <- dat %>%
  mutate(phq.change_binary =
           recode_factor(
             phq.change_binary_numeric,
             `0` = "No change",
             `1` = "Worsening",
             `2` = "Improvement"
           )
  )

@@

dat <- dat %>%
  mutate(ocir.change_binary =
           recode_factor(
             ocir.change_binary_numeric,
             `0` = "No change",
             `1` = "Worsening",
             `2` = "Improvement"
           )
  )
